Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-04 Response to reviewers.tex

%------------------------------------------------------------------------------------
\section{Comments by Reviewer \#1}

\noindent \emph{There are some issues needed to be addressed further:} \\

\noindent (1) \emph{Generally speaking, predicting sales is regarded as a regression probelm (numerical output) rather than classification (categorical one). Both CFS and RelieFF are originally designed for classification problem. When CFS is used for regression, please to introduce how to estimate correlations between each feature and output (total sales). Since RReliefF, as a variant of ReliefF, is special for regression, why do not the authors use RReliefF? }

\begin{verbatim}
In all our experiments we have applied the Weka's implementation 
of the ReliefF algorithm in the regression problems. 
This version is called "Regressional ReliefF" or "RReliefF" for 
short, which was first introduced and implemented by Robnik-Sikonja 
and Kononenko (in ref. [73] for numeric targets). 
Therefore, we have clarified this point in the text to remove 
any ambiguity.

@@

~\\
\noindent (4) \emph{It seems more reasonable to organize and write that paper according to regression viewpoint only. }

\begin{verbatim}
According to the reviewer's comment, we have addressed this issue
at the same time that comment #1, where the application procedure 
of feature selection methods for regression problems has been 
clarified. Also, we have added the ''regression'' term all along 
the paper including the description of the dataset.
\end{verbatim}

~\\
\noindent (5) \emph{It is necessary to write that paper more concisely. }

\begin{verbatim}
Following your suggestion we have reorganized some parts of the 
text and several paragraphs have been rewritten in order to make 
them shorter, clearer and to improve its comprehension.

Also, several tables have been moved to the Appendix and that
data has been presented now as the new Figure 3.

Finally, the paper has been completely revised and several 
typographic errors have been fixed.
\end{verbatim}

@@

Our main contribution is, thus, to develop a methodology to 
process book sales data in order to first find out relevant 
variables and then use these variables to process data so that 
the publisher, using them, can estimate sales and from them order 
a specific print run, instead of standard ones, which are around 
300 copies for standard books and around 5000 for those that are 
considered, in advance, best sellers.

Also, in the next-to-last paragraph, we have laid out our 
methodology and the main contributions of this paper.
\end{verbatim}

~\\
\noindent (3) \emph{Technologies related to recommend systems may have the ability to deal with this problem. The authors should add the recommend systems into the future work part. }

\begin{verbatim}
Taking into account the reviewer's comment, the recommendation 
systems have been added to the future works section, at the end 
of Section 7 (see page 19).
\end{verbatim}

~\\
\noindent (4) \emph{Some tables should be transfer to figures because there are too many tables. }

\begin{verbatim}
Following your suggestion several tables have been moved to 
the Appendix and that data has been summarized and presented 
as the new Figure 3 in order to make that numeric data clearer 
and to improve its comprehension.
\end{verbatim}

### 2016-09-04 Response to reviewers.tex

%------------------------------------------------------------------------------------
\section{Comments by Reviewer \#1}

\noindent \emph{There are some issues needed to be addressed further:} \\

\noindent (1) \emph{Generally speaking, predicting sales is regarded as a regression probelm (numerical output) rather than classification (categorical one). Both CFS and RelieFF are originally designed for classification problem. When CFS is used for regression, please to introduce how to estimate correlations between each feature and output (total sales). Since RReliefF, as a variant of ReliefF, is special for regression, why do not the authors use RReliefF? }

\begin{verbatim}
In all our experiments we have applied  WEKA's implementation 
of the ReliefF algorithm in the regression problems. 
This version is called "Regressional ReliefF" or "RReliefF" for 
short, which was first introduced and implemented by Robnik-Sikonja 
and Kononenko (in ref. [73] for numeric targets). 
Therefore, we have clarified this point in the text to remove 
any ambiguity.

@@

For CSF, estimating the correlation between attributes is 
standard linear (Pearson's) correlation. The details have 
been added to the text to clarify this point.
\end{verbatim}

~\\
\noindent (2) \emph{In sub-section 4.2, five methods are introduced, i.e.,M5P,kNN,RF,LR and SVM. In sub-section 5.1, why is MLP (multi-layer perceptron) with one hidden layer described ? For RF, how many trees are set? }

\begin{verbatim}
The current paper includes in sub-section 
''2.1. Selecting an appropriate forecasting method'' (former
sub-section 4.2) six methods: M5P, kNN, 
RF, LR, SVM and MLP.

@@

Also, as suggested by the second reviewer (see his first comment), 
the results obtained with this method have been included in the 
new version of this paper.

As far as the number of trees is concerned, in the experiments 
section, when describing the parameter settings, it has been 
mentioned that the best performance was obtained with a number of 
trees equal to 50.
\end{verbatim}

@@

~\\
\noindent (3) \emph{As we known, tree-based mehods (e.g.,M5P and RF) themselve embed feature selection procedure. That is, some features are choosen to build trees. It is not fair enough to compare five methods in Table 3. }

\begin{verbatim}
Although we agree with the reviewer's comment, and the RF and M5P 
have an embedded feature selection mechanism, we believe that it 
is unfair to compare them with the filter based feature selection 
methods we have deployed in our research. 
The idea is simply to show the decision maker what are the possible 
results when we apply one of the off-the-shelf classifiers available 
in a common open source framework such as WEKA. 
Moreover, it is not uncommon in the literature to see such comparison 
between classifiers, such as in the paper:
  M. Fernandez-Delgado, E. Cernadas, S. Barro, and D. Amorim. 2014. 
  Do we need hundreds of classifiers to solve real world 
  classification problems?. J. Mach. Learn. Res. 15, 1, pp.3133-3181
which incorporates a general comparison between all these classifiers.
\end{verbatim}
%Every response should end with changes made in the paper, even if it
%is only clarification. It is not an invitation to discussion.

### 2016-09-05 Response to reviewers.tex

\noindent
Yours sincerely,\\
The authors.

%------------------------------------------------------------------------------------
\section{Comments by Reviewer \#1}

\noindent \emph{There are some issues needed to be addressed further:} \\

\noindent (1) \emph{Generally speaking, predicting sales is regarded as a regression problem (numerical output) rather than classification (categorical one). Both CFS and RelieFF are originally designed for classification problem. When CFS is used for regression, please to introduce how to estimate correlations between each feature and output (total sales). Since RReliefF, as a variant of ReliefF, is special for regression, why do not the authors use RReliefF? }

\begin{verbatim}
In all our experiments we have applied  WEKA's implementation 
of the ReliefF algorithm in the regression problems. 
This version is called "Regressional ReliefF" or "RReliefF" for 
short, which was first introduced and implemented by Robnik-Sikonja 
and Kononenko (in ref. [73] for numeric targets). 
Therefore, we have clarified this point in the text to remove 
any ambiguity.
\end{verbatim}
% Antonio - TODO: say where is this clarification in the text (page/paragraph) and/or copy the text here
\begin{verbatim}
For CSF, estimating the correlation between attributes is 
standard linear (Pearson's) correlation. The details have 
been added to the text to clarify this point.
\end{verbatim}
% Antonio - TODO: say where is this clarification in the text (page/paragraph) and/or copy the text here

~\\
\noindent (2) \emph{In sub-section 4.2, five methods are introduced, i.e.,M5P,kNN,RF,LR and SVM. In sub-section 5.1, why is MLP (multi-layer perceptron) with one hidden layer described ?}

\begin{verbatim}
The current paper includes in sub-section 
`2.1. Selecting an appropriate forecasting method' (former
sub-section 4.2) six methods: M5P, kNN, RF, LR, SVM, MLP,
 and ELM (requested by Reviewer #2).

Moreover, as suggested by the Reviewer #2 (see his/her first comment), 
the results obtained with the two last methods have been included in 
this new version of the paper.
\end{verbatim}
% Antonio - TODO: say where are these results (table/figure/page)

~\\
\noindent (2) \emph{For RF, how many trees are set? }

\begin{verbatim}
As far as the number of trees is concerned, in the experiments 
section, when describing the parameter settings, 
it has been mentioned that the best performance was obtained with a 
number of trees equal to 50.
\end{verbatim}
% Antonio - TODO: say where is this clarification in the text (page/paragraph) and/or copy the text here

~\\
\noindent (3) \emph{As we known, tree-based methods (e.g., M5P and RF) themselves embed feature selection procedure. That is, some features are chosen to build trees. It is not fair enough to compare five methods in Table 3. }

\begin{verbatim}
Although we agree with the reviewer's comment, and the RF and M5P 
have an embedded feature selection mechanism, we believe that it 
is unfair to compare them with the filter based feature selection 
methods we have deployed in our research. 
The aim is simply to show to the decision maker what are the possible 
results when we apply one of the off-the-shelf classifiers available 
in a common open source framework such as WEKA. 
Moreover, it is not uncommon in the literature to see such comparison 
between classifiers, as in the paper:
  M. Fernandez-Delgado, E. Cernadas, S. Barro, and D. Amorim. 2014. 
  Do we need hundreds of classifiers to solve real world 
  classification problems?. J. Mach. Learn. Res. 15, 1, pp.3133-3181
which incorporates a general comparison between all these classifiers.
\end{verbatim}
%Every response should end with changes made in the paper, even if it
%is only clarification. It is not an invitation to discussion. 
% Antonio - TODO: say how this has been addressed in the paper (where it is clarified). Say if this reference has been included as new.

@@

~\\
\noindent (4) \emph{It seems more reasonable to organize and write that paper according to regression viewpoint only. }

\begin{verbatim}
The reviewer is right, thus, we have revised the whole paper referring 
to the term `regression' instead of `classification'. Moreover this have 
been also addressed solving the issue related to comment #1, where the
application procedure of feature selection methods for regression problems 
has been clarified. 
\end{verbatim}
% Antonio - CONCERN: I'm a bit afraid about the term 'organize' which I don't know if has been addressed in any way in the new version...

@@

~\\
\noindent (5) \emph{It is necessary to write that paper more concisely. }

\begin{verbatim}
Following reviewer's suggestion we have reorganized some parts of the 
text and several paragraphs have been rewritten in order to make 
them shorter, clearer and to improve its comprehension.

@@

Also, several tables have been moved to the Appendix and that
data has been presented now as the new Figure 3.

Finally, the paper has been completely revised and several 
typographic errors have been fixed.

We are very grateful for your valuable suggestions and comments. 
\end{verbatim}
% Antonio - TODO: show some examples of reduced text (page/paragraph), there will be some new figures, I think.

~\\

@@

%------------------------------------------------------------------------------------
\section{Comments by Reviewer \#2}

\noindent \emph{This paper applies some machine learning technologies to address issues related to book sales. There are some revisions that should be addressed by authors: } \\

\noindent (1) \emph{The ANN and ELM (extreme learning machine) should be added into the experiments; }

\begin{verbatim}
Following the reviewer's request, we have conducted several new experiments 
and added the results of ANN (MLP) and ELM to Tables XX, YY, ZZ and
 Figures AA, BB accordingly. 
A description of both approaches have been also included in subsection 2.1.

In addition new references has been added to the paper related to these 
methods, namely [REF_XX, REF_YY].
\end{verbatim}
% Antonio - TODO: Complete with the number of tables and figures, along with the new references

@@

~\\
\noindent (2) \emph{The authors should clarify their main contributions in the introduction parts.}

\begin{verbatim}
We have rewritten the introduction and included this new text:

"Our main contribution is, thus, to develop a methodology to 
process book sales data in order to first find out relevant 
variables and then use these variables to process data so that 
the publisher, using them, can estimate sales and from them order 
a specific print run, instead of standard ones, which are around 
300 copies for standard books and around 5000 for those that are 
considered, in advance, best sellers."

Also, in the next-to-last paragraph, we have laid out our 
methodology and clarified the main contributions of this paper 
to the state of the art.
\end{verbatim}
% Antonio - TODO: I rewritten this text, so we should copy the new one here. But I think we all should contribute to create a very good justification (see next CONCERN). :D
% Antonio - CONCERN: We should definitely write a convincing text which separates this work from existing approaches. Maybe the use of real data is a good point. And also emphasize the contribution to the SotA.

@@

~\\
\noindent (3) \emph{Technologies related to recommend systems may have the ability to deal with this problem. The authors should add the recommend systems into the future work part. }

\begin{verbatim}
Taking into account the reviewer's comment, the recommendation 
systems have been added to the future work section, at the end 
of Section 7 (see page XX).
\end{verbatim}
% Antonio - TODO: put the correct page when the text is finished. Cooy the text here.

@@

~\\
\noindent (4) \emph{Some tables should be transfer to figures because there are too many tables. }

\begin{verbatim}
Following reviewer's suggestion, several tables have been moved to 
the Appendix and that data has been summarized and presented 
as the new Figure 3 in order to make that numeric data clearer 
and to improve their comprehension.
\end{verbatim}
% Antonio - CONCERN: I think we should move ALL the results tables and include a couple of figures more. Please see my e-mail on this respect. ;)
% Antonio - TODO: Talk about the final tables and figures.

@@

~\\
\noindent (5) \emph{Graphical abstract should be added. This paper is organized well. The authors should revise their work according to above comments. }

\begin{verbatim}
We agree with the reviewer and have designed (and uploaded) a 
graphical abstract as a visual summary of the paper structure 
and the utility of the obtained results.

We would like to thank this reviewer for his/her suggestions 
and comments to improve the quality of our paper.
\end{verbatim}

~\\

@@

%------------------------------------------------------------------------------------
\section{Comments by Reviewer \#3}

\noindent \emph{There are several concerns should be considered.}\\

\noindent (1) \emph{In section introduction, this manuscript should describe the contribution of this work. }

\begin{verbatim}

********* TO WRITE ***********

\end{verbatim}
% Antonio - TODO: we can't write the same answer for two reviewers. We'll answer the same, once we have the response for the previour reviewer but in other words. ;)

@@

~\\
\noindent (2) \emph{sections 4.1 and 4.2 should be moved to section 2. }

\begin{verbatim}
Following reviewer's suggestion we have reorganized these sub-sections, 
moving them to section 2.
\end{verbatim}
% Antonio - TODO: we have also to link them properly to the new section and to remove them from the text describing Section 4 where they were... Then, say this in the response.

@@

~\\
\noindent (3) \emph{In section 4, this manuscript should show a flowchart of the proposed forecasting scheme and describe it. }

\begin{verbatim}
Taking into account the reviewer's comment, we have improved the 
description of the methodology including a flowchart (see Figure XX 
at page YY).
\end{verbatim}
% Antonio - CONCERN: I don't know if te reviewer is speaking about the whole methodology or just about the regression/forecasting part... The figure shows a rough summary of the methodology.
% Antonio - TODO: Improve the figure, which is a bit 'generic'. Put the correct figure and page.

@@

~\\
\noindent (4) \emph{In Section 5, parameter settings of 
M5P, kNN and RF also should be shown. }

\begin{verbatim}
We have improved Section 5, including the parameter settings of 
M5P, kNN and RF methods.

The authors want to express our gratitude to this reviewer 
for his/her suggestions.
\end{verbatim}
% Antonio - CONCERN: don't we also put the configuration of the rest of the methods? And say it. :D 
% Could we use a table for showing them easily?
% Antonio - TODO: say paragraph/page where they are and maybe put here the text.

\end{document}
% Antonio - TODO: Say if there are new references and include them in a final section in this letter.

### 2016-09-05 paper.tex
closing the issue about making the new Figure: Closes #52
Response to reviewers revised. See CONCERNS and TODOs
moving old tables 3 and 5 to appendix and substitute them by corresponding Figures

Correlation coefficient, error measures and time to build the model have been computed for every method. Obtained results are presented in Table \ref{tab:all_publishers_no_fs}.

\begin{table*}
\caption{Predicting Total sales for all publishers (all the features). 30 repetitions, 10-fold cross validation. Best values in bold.
\label{tab:all_publishers_no_fs}}
\centering{}%
\scalebox{0.78}{

As far as the different methods are concerned, M5P model obtained the best results, both in time and error. The advantage of M5P is that it can learn and tackle regression
% Antonio - I think we can change classification by regression. I have done. Check it out. ;)
 tasks that have high dimensionality and categorical variables efficiently. Moreover, M5P generates reproducible and comprehensible representations that provide information on the decision process and does not require human intervention either for the operation or for interpretation. Thus, it is a very suitable model be incorporated in a publishing company 
processes (as we will show in Section \ref{subsec:decision_trees}).

@@

According to Table \ref{tab:all_publishers_no_fs}, it can also be noticed that 
the Linear Regression model outperforms some other complex methods like the 
Random Forest, both in time and in obtained errors. 
%Although, Linear Regression is considered as a simple model to build, more powerful models can obtain better results in comparable time.  % I change this sentence as its meaning is 'strange'...  [pedro]
Although, Linear Regression is considered as a simple model to build, it can obtain better results than more powerful models in comparable time.

@@

\begin{table*}
\caption{Input features/variables selected by each method
\label{tab:features_selected}}
\centering{}%
\begin{tabular}{|c|c|c|c|c|}
\hline 
No. & Variable & ReliefFAttributeEval & CfsSubsetEval & SOM\\
\hline 
1 & \texttt{ret\_price} & $\checkmark$ &  & $\checkmark$\\
\hline 
2 & \texttt{subject1} & $\checkmark$ & $\checkmark$ & $\checkmark$\\
\hline 
3 &  \texttt{collection} &  &  & \\
\hline 
4 & \texttt{binding} &  &  & \\
\hline 
5 & \texttt{gifts} & $\checkmark$ &  & $\checkmark$\\
\hline 
6 & \texttt{distrib\_novelty} & $\checkmark$ &  & \\
\hline 
7 & \texttt{tot\_points\_sale} & $\checkmark$ &  & $\checkmark$\\
\hline 
8 & \texttt{tot\_points\_sale\_1st\_year} & $\checkmark$ &  & \\
\hline 
9 & \texttt{weeks\_sale} & $\checkmark$ &  & $\checkmark$\\
\hline 
10 & \texttt{print\_run} & $\checkmark$ & $\checkmark$ & $\checkmark$\\
\hline 
\end{tabular}
\end{table*}

@@

@@

\begin{table*}
\centering{}%
\caption{Predicting Total sales for all publishers based on features selected
by each method. Best values in bold.
\label{tab:results_all_publishers_fs}}
% RELIEFATTRIBUTEEVAL
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\multicolumn{7}{|c|}{\textit{ReliefAttributeEval}}\\
\hline 
 & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 89.2 $\pm$0.10 & 211.15 $\pm$22.41 & 616.35 $\pm$321.25 & 36.93 $\pm$3.41 & 47.30 $\pm$26.83 & 0.49 $\pm$0.02\\
\hline 
kNN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 &  \textbf{0.002 $\pm$0.004}\\
\hline 
RF &  \textbf{91.0 $\pm$0.05} &  \textbf{198.16 $\pm$19.50} &  \textbf{589.35 $\pm$195.80} &  \textbf{34.61 $\pm$2.27} &  \textbf{44.21 $\pm$11.63} & 3.63 $\pm$0.20\\
\hline 
LR & 86.4 $\pm$0.08 & 346.88 $\pm$25.40 & 695.90 $\pm$242.49 & 60.75 $\pm$4.55 & 53.16 $\pm$19.43 & 0.01 $\pm$0.01\\
\hline 
SVM & 84.2 $\pm$0.04 & 252.87 $\pm$33.38 & 858.26 $\pm$318.23 & 44.01 $\pm$3.04 & 62.22 $\pm$7.15 & 38.97 $\pm$5.75\\
\hline  
MLP	& 88.58 $\pm$ 0.09	& 384.94 $\pm$ 342.05	& 769.74 $\pm$ 427.35	& 67.47 $\pm$ 60.6	& 58.71 $\pm$ 34.81	& 4.9 $\pm$ 0.047\\
\hline  
ELM & 	87.55	 $\pm$ 	0.1	 & 	250.88	 $\pm$ 	28.78	 & 	677.94	 $\pm$ 	356.41	 & 	44.16	 $\pm$ 	0.05	 & 	50.86	 $\pm$ 	0.24	 & 	0.1106	 $\pm$ 	0.02\\
\hline

\end{tabular}
}
% CFSSUBEVAL
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\multicolumn{7}{|c|}{\textit{CfsSubEval}}\\
\hline
 & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P &  \textbf{87.0 $\pm$0.09} &  \textbf{266.78 $\pm$23.12} &  \textbf{662.32 $\pm$245.27} &  \textbf{46.66 $\pm$3.25} &  \textbf{50.9 $\pm$20.35} & 0.41 $\pm$0.04\\
\hline 
kNN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 &  \textbf{0.001 $\pm$0.001}\\
\hline 
RF & 85.0 $\pm$0.11 & 278.42 $\pm$23.07 & 714.13 $\pm$278.65 & 48.71 $\pm$3.43 & 55.26 $\pm$24.41 & 2.48 $\pm$0.13\\
\hline 
LR & 85.9 $\pm$0.06 & 356.35 $\pm$22.43 & 708.06 $\pm$195.15 & 62.42 $\pm$4.22 & 53.97 $\pm$14.05 & 0.01 $\pm$0.001\\
\hline 
SVM & 86.0 $\pm$0.06 & 288.47 $\pm$30.32 & 817.56 $\pm$253.24 & 50.30 $\pm$2.38 & 60.27 $\pm$5.68 & 32.73 $\pm$5.74\\
\hline
MLP	& 87.26 $\pm$ 0.1	& 420.02 $\pm$ 491.51	& 771.6 $\pm$ 514.03	& 73.6 $\pm$ 87.04	& 60.09 $\pm$ 46.83	& 1.08 $\pm$ 0.019\\
\hline
ELM & 	85.91	 $\pm$ 	0.12	 & 	282.56	 $\pm$ 	28.36	 & 	692.59	 $\pm$ 	281.38	 & 	49.87	 $\pm$ 	0.06	 & 	53.74	 $\pm$ 	0.25	 & 	0.0095	 $\pm$ 	0.02\\
\hline

After applying the feature selection process, we have run the same
forecasting models as in Section \ref{subsec:results_all_publishers}
for the whole dataset (all the publishers), but considering only the
selected features by each method. The results are shown in Table
\ref{tab:results_all_publishers_fs}. Examining the obtained results
for each feature selection method, it can be seen that RFE got the
best results compared to SOM and CSE. It can be noticed also that we
obtain better performance using M5P, kNN and RF with the set of features
selected by RFE than using all features. %Better publish results in
                                %the same table or refer to the table
                                %where it was published. Is this
                                %difference statistically significant?
                                %- JJ
As expected, in general, all feature selection methods have reduced the training time needed to build the forecasting methods. This is because they reduced the considered features and mainly because they excluded the categorical features, which are the hardest to be managed (they have many possible values). On the other side, CSE and SOM did not perform as good as RA. This could be explained due to the extensive reduction made by CSE and due to the `subjective' (but not so accurate) human intervention in the case of SOM.

@@

>>>>

Correlation coefficient, error measures and time to build the model have been 
computed for every method. Obtained results are presented in 
Figure \ref{fig:all_publishers_no_fs}
(detailed numeric results can be shown in Table Table \ref{tab:all_publishers_no_fs}
in the appendix of tables at the end of this paper).

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.35]{./imgs/prediction_all_publisher_all_features_Table3.eps}
\end{center}
\caption{Predicting \texttt{total\_sales} for all publishers (all the features). 30 repetitions, 10-fold cross validation.}
\label{fig:all_publishers_no_fs}
\end{figure*}

As far as the different methods are concerned, M5P model obtained the best results, 
both in time and error. The advantage of M5P is that it can learn and tackle 
regression tasks that have high dimensionality and categorical variables efficiently. 
Moreover, M5P generates reproducible and comprehensible representations that 
provide information on the decision process and does not require human intervention 
either for the operation or for interpretation. Thus, it is a very suitable model 
be incorporated in a publishing company processes (as we will show in 
Section \ref{subsec:decision_trees}).

@@

According to Figure \ref{fig:all_publishers_no_fs}, it can also be noticed that 
the Linear Regression model outperforms some other complex methods like the 
Random Forest, both in time and in obtained errors. 
%Although, Linear Regression is considered as a simple model to build, more powerful models can obtain better results in comparable time.  % I change this sentence as its meaning is 'strange'...  [pedro]
Although, Linear Regression is considered as a simple model to build, it can obtain better results than more powerful models in comparable time.

@@

@@

\begin{table*}
\caption{Input features/variables selected by each method
\label{tab:features_selected}}
\centering{}%
{\footnotesize
\begin{tabular}{|c|c|c|c|c|}
\hline 
No. & Variable & ReliefFAttributeEval & CfsSubsetEval & SOM\\
\hline 
1 & \texttt{ret\_price} & $\checkmark$ &  & $\checkmark$\\
\hline 
2 & \texttt{subject1} & $\checkmark$ & $\checkmark$ & $\checkmark$\\
\hline 
3 &  \texttt{collection} &  &  & \\
\hline 
4 & \texttt{binding} &  &  & \\
\hline 
5 & \texttt{gifts} & $\checkmark$ &  & $\checkmark$\\
\hline 
6 & \texttt{distrib\_novelty} & $\checkmark$ &  & \\
\hline 
7 & \texttt{tot\_points\_sale} & $\checkmark$ &  & $\checkmark$\\
\hline 
8 & \texttt{tot\_points\_sale\_1st\_year} & $\checkmark$ &  & \\
\hline 
9 & \texttt{weeks\_sale} & $\checkmark$ &  & $\checkmark$\\
\hline 
10 & \texttt{print\_run} & $\checkmark$ & $\checkmark$ & $\checkmark$\\
\hline 
\end{tabular}
}
\end{table*}

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.35]{./imgs/prediction_all_publisher_Table5.eps}
\end{center}
\caption{Predicting \texttt{total\_sales} for all publishers based on features selected by each method.}
\label{fig:results_all_publishers_fs}
\end{figure*}

@@

After applying the feature selection process, we have run the same
forecasting models as in Section \ref{subsec:results_all_publishers}
for the whole dataset (all the publishers), but considering only the
selected features by each method. 
The results are shown in Figure \ref{fig:results_all_publishers_fs} 
(detailed numeric results can be shown in Table \ref{tab:results_all_publishers_fs}
in the appendix of tables at the end of this paper).
Examining the obtained results for each feature selection method, 
it can be seen that RFE got the best results compared to SOM and CSE. 
It can be noticed also that we obtain better performance using M5P, 
kNN and RF with the set of features selected by RFE than using all features. 
                                %Better publish results in
                                %the same table or refer to the table
                                %where it was published. Is this
                                %difference statistically significant?
                                %- JJ
As expected, in general, all feature selection methods have reduced the training 
time needed to build the forecasting methods. This is because they reduced the 
considered features and mainly because they excluded the categorical features, 
which are the hardest to be managed (they have many possible values). 
On the other side, CSE and SOM did not perform as good as RA. 
This could be explained due to the extensive reduction made by CSE and due to 
the `subjective' (but not so accurate) human intervention in the case of SOM.

@@

%--------------- old Tables 3, 5 (before revision)

\begin{table*}
\caption{Predicting \texttt{total\_sales} for all publishers (all the features). 30 repetitions, 10-fold cross validation. Best values in bold.
\label{tab:all_publishers_no_fs}}
\centering{}%
\scalebox{0.78}{

\begin{table*}
\centering{}%
\caption{Predicting \texttt{total\_sales} for all publishers based on features selected by each method. Best values in bold.
\label{tab:results_all_publishers_fs}}
% RELIEFATTRIBUTEEVAL
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\multicolumn{7}{|c|}{\textit{ReliefAttributeEval}}\\
\hline 
 & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 89.2 $\pm$0.10 & 211.15 $\pm$22.41 & 616.35 $\pm$321.25 & 36.93 $\pm$3.41 & 47.30 $\pm$26.83 & 0.49 $\pm$0.02\\
\hline 
kNN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 &  \textbf{0.002 $\pm$0.004}\\
\hline 
RF &  \textbf{91.0 $\pm$0.05} &  \textbf{198.16 $\pm$19.50} &  \textbf{589.35 $\pm$195.80} &  \textbf{34.61 $\pm$2.27} &  \textbf{44.21 $\pm$11.63} & 3.63 $\pm$0.20\\
\hline 
LR & 86.4 $\pm$0.08 & 346.88 $\pm$25.40 & 695.90 $\pm$242.49 & 60.75 $\pm$4.55 & 53.16 $\pm$19.43 & 0.01 $\pm$0.01\\
\hline 
SVM & 84.2 $\pm$0.04 & 252.87 $\pm$33.38 & 858.26 $\pm$318.23 & 44.01 $\pm$3.04 & 62.22 $\pm$7.15 & 38.97 $\pm$5.75\\
\hline  
MLP	& 88.58 $\pm$ 0.09	& 384.94 $\pm$ 342.05	& 769.74 $\pm$ 427.35	& 67.47 $\pm$ 60.6	& 58.71 $\pm$ 34.81	& 4.9 $\pm$ 0.047\\
\hline  
ELM & 	87.55	 $\pm$ 	0.1	 & 	250.88	 $\pm$ 	28.78	 & 	677.94	 $\pm$ 	356.41	 & 	44.16	 $\pm$ 	0.05	 & 	50.86	 $\pm$ 	0.24	 & 	0.1106	 $\pm$ 	0.02\\
\hline

\end{tabular}
}
% CFSSUBEVAL
\resizebox{12cm}{!}{
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\multicolumn{7}{|c|}{\textit{CfsSubsetEval}}\\
\hline
 & $R$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P &  \textbf{87.0 $\pm$0.09} &  \textbf{266.78 $\pm$23.12} &  \textbf{662.32 $\pm$245.27} &  \textbf{46.66 $\pm$3.25} &  \textbf{50.9 $\pm$20.35} & 0.41 $\pm$0.04\\
\hline 
kNN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 &  \textbf{0.001 $\pm$0.001}\\
\hline 
RF & 85.0 $\pm$0.11 & 278.42 $\pm$23.07 & 714.13 $\pm$278.65 & 48.71 $\pm$3.43 & 55.26 $\pm$24.41 & 2.48 $\pm$0.13\\
\hline 
LR & 85.9 $\pm$0.06 & 356.35 $\pm$22.43 & 708.06 $\pm$195.15 & 62.42 $\pm$4.22 & 53.97 $\pm$14.05 & 0.01 $\pm$0.001\\
\hline 
SVM & 86.0 $\pm$0.06 & 288.47 $\pm$30.32 & 817.56 $\pm$253.24 & 50.30 $\pm$2.38 & 60.27 $\pm$5.68 & 32.73 $\pm$5.74\\
\hline
MLP	& 87.26 $\pm$ 0.1	& 420.02 $\pm$ 491.51	& 771.6 $\pm$ 514.03	& 73.6 $\pm$ 87.04	& 60.09 $\pm$ 46.83	& 1.08 $\pm$ 0.019\\
\hline
ELM & 	85.91	 $\pm$ 	0.12	 & 	282.56	 $\pm$ 	28.36	 & 	692.59	 $\pm$ 	281.38	 & 	49.87	 $\pm$ 	0.06	 & 	53.74	 $\pm$ 	0.25	 & 	0.0095	 $\pm$ 	0.02\\
\hline
